Multi-resolution Neural Field Estimation

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
minor correctin

\mike{The framework makes two key assumptions about the cortex: a linear activation function and stationary dynamics. Our main aim for this framework is to relax these assumptions using the multi-resolution decomposition. \dean{(our main aim wasn't really to relax the assumptions. if it was, we failed.)} While the decomposition itself holds, efficiently performing nonlinear smoothing in the much larger state space remains a challenge. Additional avenues for future work include extending the model to capture a second order synaptic response kernel, and time delays at lower spatial resolutions.  The estimation techniques should also be extended to deal with spatial and temporal heterogeneity in the kernel. Finally, the majority of our current work involves applying this framework to collected data, primarily for the use of seizure detection and mitigation.}

% \cut{In order to apply the framework to real data some assumptions must be made, such as stationarity of the parameters over the estimation period. Perhaps the most critical assumption is that the model provides an apt description of the cortical dynamics. The authors acknowledge that there is, and will always be, a discrepancy between the model and cortex. Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation. The key development in this paper is the multi-resolution decomposition forming the state-space model. The decomposition holds for more sophisticated nonlinear forms of the field equations, where the unscented RTS smoother should be used in the E-step of the estimation algorithm.}

>>>>

 \mike{The framework makes two key assumptions about the cortex: a linear activation function and stationary dynamics. Our main aim for this framework is to relax these assumptions using the multi-resolution decomposition. \dean{(our main aim wasn't really to relax the assumptions. if it was, we failed.)} While the decomposition itself holds, efficiently performing nonlinear smoothing in the much larger state space remains a challenge. Additional avenues for future work include extending the model to capture a second order synaptic response kernel, and time delays \parham{at lower spatial resolutions}.  The estimation techniques should also be extended to deal with spatial and temporal heterogeneity in the kernel. Finally, the majority of our current work involves applying this framework to collected data, primarily for the use of seizure detection and mitigation.}

 \cut{In order to apply the framework to real data some assumptions must be made, such as stationarity of the parameters over the estimation period. Perhaps the most critical assumption is that the model provides an apt description of the cortical dynamics. The authors acknowledge that there is, and will always be, a discrepancy between the model and cortex. Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation. The key development in this paper is the multi-resolution decomposition forming the state-space model. The decomposition holds for more sophisticated nonlinear forms of the field equations, where the unscented RTS smoother should be used in the E-step of the estimation algorithm.}
